---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


## Data Discovery
  The data that I will be using for my Portfolio Project is provided by Amazon. Their datasets are hosted on AWS for anyone to download. With how many products Amazon sells, observations from any one catagory of products is out of the scope of this class. I chose the camera category but still needed to cut down on my sample size so I took Amazons original CSV file, sorted it by each products parent_id and then pulled the first 5000 observations. This boils down to 5000 reviews for 435 different camera products (This file is hosted as a CSV on my github). I have always been curious of big data and other than Google, Amazon seems to store a ton of data. While my work will not be able to look at it all, reviewing a small portion of Amazons store reviews will hopefully give insite as to why Amazon is so popular.
  
## Data Preparation
Start of the Project 
install packages

```{r}
library("tidyverse")
library("dplyr")
library("tidyr")
library("readr")
library("ggplot2")

```

add the dataset
```{r}
Amazon_Ratings <- read_csv("https://raw.githubusercontent.com/NathanLovell/DataScience-Nathan-Lovell/master/5000_Rows.csv")
```

rename columns
```{r}
#colnames(Amazon_Ratings)[colnames(Amazon_Ratings) == "vine"] <- "vine_verified"
colnames(Amazon_Ratings)

```




create additional tables as needed

```{r}
Review <- tibble(review_id=Amazon_Ratings$review_id, customer_id=Amazon_Ratings$customer_id, product_id=Amazon_Ratings$product_id, star_rating=Amazon_Ratings$star_rating, helpful_votes=Amazon_Ratings$helpful_votes, total_votes=Amazon_Ratings$total_votes, vine_verified=Amazon_Ratings$vine, verified_purchase=Amazon_Ratings$verified_purchase, review_title=Amazon_Ratings$review_headline, review_body=Amazon_Ratings$review_body, review_date=Amazon_Ratings$review_date)
Product <- tibble(product_id=Amazon_Ratings$product_id, parent_id=Amazon_Ratings$product_parent, description=Amazon_Ratings$product_title, category=Amazon_Ratings$product_category)

colnames(Review)
colnames(Product)
```


remove duplicate products based on product id

```{r}
Product <- distinct(Product, Product$product_id, .keep_all = TRUE)
```


columns to factors

```{r}

```


visualizations and connections

```{r}

```



